\bf\mftitle

### 2011-02-01 doc/jInfer/basicigg/basicigg.tex
Documentation: BasicIGG

This is a rather na\"{i}ve implementation of an XPath processor. It registers itself into \emph{query} input folder, \emph{xpath} file extension (text file containing one XPath query per line) and declares it cannot handle other file extensions.\\
To parse XPath queries, standard support present in JDK is used. The relevant \code{XPathHandler} is the \code{XPathHandler} class.\\
% TODO vektor Explain how it works...

>>>>

This is a rather na\"{i}ve implementation of an XPath processor. It registers itself into \emph{query} input folder, \emph{xpath} file extension (text file containing one XPath query per line) and declares it cannot handle other file extensions.\\
To parse XPath queries, standard support present in JDK is used. The relevant \code{XPathHandler} is the \code{XPathHandlerImpl} class.\\
While the exact process by which \code{XPathHandlerImpl} creates the IG from a series of XPath events is an interesting coding exercise, its description is beyond the scope and requirements of this document.
